Open Linked Social Data for Scientific Benchmarking

### 2016-06-30 paper.tex
first outline

\subsection{Benchmarking in the analysis of complexity}
%
Every designer of a new method wants to know how good the proposed method is in comparison with others.
Usually such comparison is made by run different methods on some commonly used benchmark datasets and use some of the proposed evaluation measures, e.g.,~\cite{Dreiseitl200128,Cooper1997107,Douglas2011544,Kampichler2010441,DBLP:journals/corr/abs-1301-7401,steinbach00comparison,Kakkar2014}.
%
% karate club, whatelse?

@@

\section{Results: data outline}
\label{outline}

>>>>

\subsection{Benchmarking in the analysis of complexity}
%
Karate club, whatelse?

@@

\section{Results}
\label{outline}
\subsection{Data outline}
\subsection{Software tools}
\subsection{SPARQL queries}
